%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', 
'11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 
'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 
'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 
'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' 
for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page 
numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, 
replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your 
resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[
    scale=0.75,
    top=1.0in,
    bottom=0.6in
]{geometry}



%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the 
column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to 
force the width allocated to your name and avoid line breaks. be careful though, the length is 
normally calculated to avoid any overlap with your personal info; use this at your own 
typographical risks...

\usepackage{import}

% personal data
\name{Tamas}{Barabas}
\title{Programmer}                               % optional, remove / comment the line if not 
wanted
%\address{my address, line 1, line 2, line 3, postcode}{}{}% optional, remove / comment the line 
if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44 75879 22003}                   % optional, remove / comment the line if not 
wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not 
wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not 
wanted
\email{tamas.b.barabas@gmail.com}                               % optional, remove / comment the 
line if not wanted
\social[linkedin]{TamasBarabas}   
\social[github]{TamasBarabas}                         % optional, remove / comment the line if 
not wanted
 
%\extrainfo{additional information}                 % optional, remove / comment the line if not 
wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not 
wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame 
around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not 
wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if 
you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}



%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

%\small{Undergraduate electrical and electronic engineer completing the final year of a master's 
degree. Passionate about science, with strong technical, business, and interpersonal skills for 
working in a team and successfully completing a project.}

\section{Technical Skills Summary}

\vspace{6pt}

\begin{itemize}

\item \textbf{Programming Languages:}  C\#, JavaScript, Java, C++
%Proficient in: C, C++, Python, Matlab, Arduino, TeX \\ Also basic ability with: Assembly, VBA, 
VHDL.

\vspace{6pt}

\item \textbf{Web:} JavaScript, React.js, jQuery, HTML, CSS

\vspace{6pt}

\item \textbf{Databases:} MS SQL Server, MySQL, Oracle, MongoDB

\vspace{6pt}

\item \textbf{Tools, Frameworks:} Node.js, ASP.NET, MVC, RabbitMQ, GIT, TFS

\vspace{6pt}

\item \textbf{Operating Systems:} Linux, Windows, OSX, VMS

\vspace{6pt}

\item \textbf{Design:} DDD, Event sourcing, CQRS, Microservices

\end{itemize}

\section{Professional experience}

\vspace{6pt}



\cventry[0em]{June 2016 - Present}{System Engineer}{American Express GBT (form. Banks 
Sadler)}{London, United Kingdom}{}\endcsname
\begin{itemize}
{\item{\vspace{pt}I am responsible for maintaining our client-facing system. It has multiple 
modules what administrators can turn on or off on demand. Modules include registration for 
events, where delegates answer questions related to the event, on-screen signature, timetable, 
multimedia file management, notifications.}}
{\item{\vspace{3pt}Started to create modules in .NET Core and React + Redux frontend}}
{\item{\vspace{3pt}Worked on the inhouse software used by event management and venue find teams. 
Events, bookings, services, service provides, related documents are registered in the system.}}
{\item{\vspace{3pt}Created Logi reports, the data is collected from the registration database. 
Designed generic reports where the user can select fields on demand.}}
{\item{\vspace{3pt}Set up TFS Build \& Deployment system.}}
\end{itemize}
\vspace{6pt}
{\textit{C\#, ASP.NET MVC, Microsoft SQL Server, Knockout, React, Logi analytics, TFS}
\vspace{12pt}}

\cventry[0em]{Jan 2013 – June 2016}{Software Engineer, Content Integration Engineer}{FactSet 
Europe LTD}{London, United Kingdom}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}Member of the Content Integration Engineering team, the purpose of our tools 
is to parse data, load into our databases, process it, and make it available for clients.}}
{\item{\vspace{3pt}Maintained our legacy system, written in C++, using NO-SQL database 
technology.}}
{\item{\vspace{3pt}Implemented new modules for the current content integration system, written 
in C\#, using Microsoft SQL Server.}}
{\item{\vspace{3pt}I worked on the integration tool of a new dataset. I was solely responsible 
for the design, implementation and the maintenance of the system. I was working in collaboration 
with our product developer team based in the US.}}
{\item{\vspace{3pt}Maintained the web interface of our timestamp logger tool, which is written 
in Ruby on Rails and MySQL.}}
\end{itemize}
\vspace{6pt}
{\textit{C\#, C++, Microsoft SQL Server, SSIS, SSRS, Ruby, Ruby on Rails, Perl, MySQL, ASP.NET, 
Perforce, Jenkins, Linux, VMS}
\vspace{12pt}}


\newpage

\cventry[0em]{Sept 2010 – Feb 2011}{Web Designer, developer, contractor}{OTKA}{Budapest, 
Hungary}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}Designed and implemented the OTKA company's webpage, in collaboration with 
the management of the company and the graphic designer of the public interface I used my CMS 
system which I designed to be generic, and reusable for other websites.}}
\end{itemize}
\vspace{6pt}
{\textit{PHP, Doctrine, JavaScript, jQuery, CSS, Smarty, MySQL, TinyMce, jsTree, superfish menu}
\vspace{12pt}}

\cventry[0em]{Sept 2010 - June 2011}{Java lecturer}{Liaiskola high school}{Budapest, 
Hungary}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}Gave lecture called ‘Introduction to programming’ using my own lecture 
material}}
\end{itemize}
\vspace{6pt}
{\textit{http://barii.web.elte.hu/}
\vspace{12pt}}



\cventry[0em]{Nov 2009 - Oct 2010}{PHP and Flash developer}{PPSystems}{Budapest, 
Hungary}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}Implemented student association's web page. I used some existing source code 
provided by the company.}}
{\item{\vspace{3pt}Added new features for existing online shopping web application.}}
\end{itemize}

\vspace{6pt}
{\textit{PHP, JavaScript, jQuery, CSS, Smarty, MySQL, Flash}
\vspace{12pt}}


%\item{\cventry{2009--2011}{Waiter, Catering and Banqueting}{Lavender Best Western Park Hall 
Hotel}{Charnock Richard}{}{\vspace{3pt}\hspace{3pt}I worked for three years as a team leader 
providing silver service at weddings, stag/hen nights, and business conferences. I was often 
trusted with other jobs such as setting up conference rooms, moving beds around the hotel, and 
guiding big groups of customers to their rooms. As a team leader I would delegate tasks to a 
team of about 5 people, often new staff who needed training, and lead the group to service. 
During this time I worked in a highly professional manner and was focused to provide excellent 
customer service, even during high stress functions and events.}}

%\vspace{6pt}

%\item{\cventry{January 2008}{Assistant Electrician}{Ryan 
Electricals}{Southport}{}{\vspace{3pt}I spent a week working as an assistant electrician as part 
of my high school work experience. My roles included wiring plugs, tidying, and assisting with 
household electrical repairs and fittings.}}


\section{Education}

%\vspace{5pt}

%\subsection{Academic Qualifications}

%\vspace{5pt}



\cventry[-0.6em]{Oct 2011 -- Aug 2012}{MSc Computational and Software Techniques in 
Engineering}{Cranfield University}{Bedfordshire, United Kingdom }{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}\textbf{Thesis: }‘Simulation of a Peer-to-Peer network‘
Implementation of the Chord distributed hash table algorithm with SimGrid toolkit and simulator 
developed using C language and Linux}}
\end{itemize}

\vspace{6pt}
\hspace{50pt}\textit{(Double degree program in conjunction with Eotvos Lorand University)}
\vspace{6pt}

\cventry[-0.6em]{Feb 2010 -- Aug 2012}{MSc Computer Science}{Eotvos Lorand University}{Budapest, 
Hungary}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}\textbf{Thesis: }‘Simulation of a Peer-to-Peer network’ (in progress with 
Cranfield University)}}
\end{itemize}
\vspace{6pt}

\cventry[-0.6em]{Oct 2005 -- Jan 2010}{BSc Computer Science}{Eotvos Lorand University}{Budapest, 
Hungary}{}\endcsname
\begin{itemize}
{\item{\vspace{3pt}\textbf{Thesis: }‘Implementation of the HOTEL board game’
Designed and developed a desktop application using Java Swing, sockets. In addition the human 
players could be replaced by AI players.}}

\end{itemize}

\vspace{6pt}

\subsection{Qualifications and online courses}

\vspace{5pt}

\cventry[-1.0em]{}{}{Udemy - Andrew Mead - Node.js}{2018}{}
{}

\cventry[-1.0em]{}{}{Udemy - Andrew Mead - React}{2018}{}
{}

\cventry[-1.0em]{}{}{Coursera - MongoDb for Developers}{May 2016}{}
{}

\cventry[-1.0em]{}{}{Oracle Fusion Middleware Developments}{May 2009}{}
{}




%\vspace{3pt}

%\small{I am part of a team developing a 5ft autonomous humanoid robot. This ambitious project 
requires strong team-working skills and high technical ability. I work well as part of the team, 
contributing in group discussions and taking initiative to set myself tasks when the next stage 
of the project is not clear. Given the role of electronics supervisor I am responsible for 
setting goals and ensuring all the electronic system designs are realised on time and meet the 
specifications of the project.}}



%\item{\textbf{3rd year individual project:} \textit{'Artificial Neural Network Approach to 
Source Localisation in Radiation Portal Monitoring'}

%\vspace{3pt}

%\small{This challenging project took place over the entirety of my third year. It required 
excellent planning and organisational skills, and the ability to teach myself an entirely new 
and complex subject. The project was a success, with the system being able to localise a 
radioactive source down to $ 3 cm$ within a $ 600 m^3$ sensor array. This project has been 
suggested for publication by my supervisor.}}

%\vspace{6pt}

%\item{\textbf{Industrial Project with Leyland Motors Ltd:}\textit{'Development of a Facility to 
Ensure the Achievement of Torque Parameters for a Specific Axle Configuration'}

%\vspace{3pt}

%\small{In the 3rd year of my course I spent a week completing an industrial project for Leyland 
Motors. I worked with a team operating as consultants for a particular problem the company was 
having. During this project I was working in a professional environment, and co-operating with 
various managers and engineers to create a design that met the requirements of the problem.}}

%\end{itemize}

%\section{Interests and extra-curricular activity}

%\vspace{6pt}

%\begin{itemize}

%\item{I was a "fresher representative" in my 2nd and 3rd years of university, this required me 
to guide, look after, and ensure that a particular flat of first years have a good time in their 
first week, and feel consoled in what for most of them is there first time living away from 
home. We were responsible for the safety and wellbeing of the group of first years during the 
first week, and during this time I made good friends with all of them.}

%\vspace{6pt}

%\item{I am a member of a number of university societies. I was also the vice president and 
co-founder of the flash mob society. My roles in this included recruiting members, in which 
during "fresher's fair" we enlisted over 200 new members. This was regarded as very successful, 
considering other societies averaged around 50. I also appeared in an interview on the 
university television station, set up a society bank account, and helped organise the events. 
One of these events was featured in the local newspaper.}

%\vspace{6pt}

%\item{I am also an avid hiker, having completed the national 3 peaks challenge last summer. 
Other interest include guitar, which I am self-taught, and home brewing.}

%\end{itemize}

%\section{References}

%\vspace{6pt}
 
%\begin{itemize}

%\item{Up to 4 references available on request}

%\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% 
CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------
\pagenumbering{gobble}
\end{document}


%% end of file `template.tex'.

